Downloading data

### 2023-05-21 episodes/downloading-data.Rmd
A few typos and imprecisions fixed

Use the `mkdir` command to make the following directories:  
molepi
molepi/docs  
molepi/data  
molepi/results

@@

Let's download data for two *M. tuberculosis* genomes with a `for` loop. Here is an example, but you may choose two other samples (see below).

```bash
$ cd molepi/data
$ for files in ERR029/ERR029207 ERR029/ERR029206
do 
wget "ftp://ftp.sra.ebi.ac.uk/vol1/fastq/"${files}"/*fastq.gz"
done
```

This will run for a while (maybe 5 minutes).

The command for downloading all data (*Don't do this.*) would be:

@@

The main command (`wget`) is commented out (prefixed with `#`) to prevent unintentional use.

>>>>

Use the `mkdir` command to make the following directories:  
```
molepi
molepi/docs  
molepi/data  
molepi/results
```

@@

Let's download data for the *M. tuberculosis* genomes with a `for` loop. We would use the following loop to download all samples:

@@

Note the `#` that prevents the `wget` command from running: that would take too long, so we're downloading only one (that's a short loop!):
```bash
$ cd molepi/data
$ for files in ERR029/ERR029206 
do 
wget "ftp://ftp.sra.ebi.ac.uk/vol1/fastq/"${files}"/*fastq.gz"
done
```

This will run for a little while (hopefully no more than 5-10 minutes).
